Methods for Large Scale Learning to Rank

### 2014-04-14 report/Chapters/BenchmarkResults.tex
benchmarkresults inleiding

\label{chap:benchmark_results}
This chapter describes benchmark characteristics like collection size and features and gives an overview of the performance of different Learning-to-Rank methods. Performance differences for a given Learning-to-Rank method are explained in terms of differences in benchmark characteristics. This chapter is concluded with a selection of Learning-to-Rank methods to include in the experiments.\\

Benchmarking datasets enable fair comparisons of ranking models over a fixed set of documents and queries. The approach of using fixed benchmarking datasets to compare the performance of Information Retrieval systems under equal circumstances has been the standard evaluation methodology in the Information Retrieval field since the release of the Cranfield collection \cite{Cleverdon1966}.
\section{Yahoo! Learning to Rank Challenge}
Yahoo's observation that all existing benchmark datasets were too small to draw reliable conclusions prompted Yahoo to release two internal datasets from Yahoo! search. Datasets used at commercial search engines are many times larger than available benchmark datasets. Yahoo! published a subset of their own commercial training data and launched a Learning-to-Rank competition based on this data. The Yahoo! Learning to Rank Challenge \cite{Chapelle2011a} is a public Learning-to-Rank competition which took place from March to May 2010, with the goal to promote the datasets and encourage the research community to develop new Learning-to-Rank algorithms.\\

>>>>

\label{chap:benchmark_results}
Benchmark datasets enable fair comparisons of ranking models over a fixed set of documents and queries. The approach of using fixed benchmark datasets to compare the performance of Information Retrieval systems under equal circumstances has been the standard evaluation methodology in the Information Retrieval field since the release of the Cranfield collection \cite{Cleverdon1966}.\\

This chapter describes benchmark characteristics, e.g. collection size and features, of Learning-to-Rank benchmark collections and datasets and gives an overview of the performance of baseline algorithms on these collections and datasets.\\

\section{Yahoo! Learning to Rank Challenge}
Yahoo's observation that all existing benchmark datasets were too small to draw reliable conclusions prompted Yahoo to release two internal datasets from Yahoo! search. Datasets used at commercial search engines are many times larger than available benchmark datasets. Yahoo! published a subset of their own commercial training data and launched a Learning-to-Rank competition based on this data. The Yahoo! Learning to Rank Challenge \cite{Chapelle2011a} is a public Learning-to-Rank competition which took place from March to May 2010, with the goal to promote the datasets and encourage the research community to develop new Learning-to-Rank algorithms.\\
